Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2016-11-08 WSSSPE4_report/survey_details.tex
moving survey figures, fixing figure latex
adding some captions to figures and todos for someone with latex skills and time

@@

@@

@@

@@

>>>>

%Figures have been inserted with little/no formatting.  
%Figures are in *.png but can be remade to other formats 
\todo{should remove these 3 figure borders in the figure source, then in LaTeX place them all in row of fix to use multifig}
\begin{figure}[h!]
\includegraphics[width=0.3\textwidth]{figures/SurveyFig1}
\caption{The plenary sessions had a good mix of topics and speakers.
\label{fig:SFig1}}
\end{figure}
\begin{figure}[h!]
\includegraphics[width=0.3\textwidth]{figures/SurveyFig2}
\caption{The balance was right between talks, panels, and lightning talks.
\label{fig:SFig2}}
\end{figure}
\begin{figure}[h!]
\includegraphics[width=0.3\textwidth]{figures/SurveyFig3}
\caption{There was sufficient time for discussion.
\label{fig:SFig3}}
\end{figure}

@@

\todo{move table and figure to be in a single row}

@@

\todo{remove figure border}
\begin{figure}[h!]
\includegraphics{figures/SurveyFig4}
\caption{What part of the meeting was the most valuable?
\label{fig:SFig4}}
\end{figure}

@@

\todo{remove figure border}
\begin{figure}[h]
\includegraphics{figures/SurveyFig5}
\caption{Would you be interested in joining a professional society focused around the topics of WSSSPE?
\label{fig:SFig5}}
\end{figure}

@@

\todo{remove figure border}
\begin{figure}[h]
\includegraphics{figures/SurveyFig6}
\caption{Will you be part of a working group  with colleagues going forward  on a topic addressed at WSSSPE?
\label{fig:SFig6}}
\end{figure}
